% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.25in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% Font Awesome for icons in Latex / PDFLatex

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%college
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% make functional tabs
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.11\textwidth}\rlap{#1}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Barron Roth}}

broth@bu.edu\ \ \textbullet
\ \ @iamBarronRoth\ \ \textbullet
\ \ BarronRoth.com\ \ \textbullet
\ \ linkedin.com/in/barronlroth

\end{center}

\hrule
\vspace{-0.9em}

\subsection*{Education}

\begin{itemize}
	\parskip=0.001em
	
	\item 
	\headerrow
	{\textbf{Boston University}}
	{\textbf{Boston, MA}}
	\headerrow
	{\emph{College of Engineering, B.Sc. Computer Engineering, Concn. Technology Innovation}}
	{\emph{Dec. 2016}}
	
	\item 
	\headerrow
	{\textbf{Pine Crest School}}
	{\textbf{Fort Lauderdale, FL}}
	\headerrow
	{\emph{ACT: 33 (99\%ile), Honor Roll, National Merit Commended \& Hispanic Recognition Program Scholar}}
	{\emph{Class of 2012}}
	
\end{itemize}


\hrule
\vspace{-0.9em}


\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em
	
	\item
	\headerrow
	{\textbf{Tablelist}}
	{\textbf{Boston, MA}}
	\\
	\headerrow
	{\emph{Software Engineering Intern}}
	{\emph{Summer 2015}}
	\begin{itemize*}
		\item Developed an improved event system for Tablelist iOS application containing relevant API data using \textit{Swift}.
		\item Initiated migration of iOS back-end from the Core Data framework to the Realm Mobile Database in \textit{Swift 2.0}.
		\item Led product QA efforts by targeting specific user demographics collected through scripts ran on user database.
		\item Provided nightlife photography \& video for Tablelist events at New York City \& Boston partner venues.
		
	\end{itemize*}
	
	\item
	\headerrow
	{\textbf{Advanced Micro Devices (AMD)}}
	{\textbf{Austin, TX}}
	\\
	\headerrow
	{\emph{Semi-Custom Product Development Co-Op Engineer}}
	{\emph{Spring 2014}}
	\begin{itemize*}
		\item Tested coverage \& compliance of semi-custom APUs using Automated Test Equipment at extreme conditions.
		\item Developed scripting program using \textit{Perl} to facilitate big data aggregation \& determine trends in testing results.
		\item Participated in meetings with customer (Microsoft) to identify \& document APU architectural performance issues.
		\item Spearheaded revival of AMD University Student Center program by photographing intern headshots \& activities.
		
	\end{itemize*}
	
	\item
	\headerrow
	{\textbf{Downtyme, Inc.}}
	{\texttt{downty.me/}}
	\\
	\headerrow
	{\emph{Co-Founder \& Program Manager}}
	{\emph{Nov. 2013 -- Present}}
	\begin{itemize*}
		\item Developed concept for iOS \& Android social-productivity app and led product team through
		\item Co-founded corporation to eventual funding by Rough Draft Ventures.
	\end{itemize*}
	
	%Luxe St
	\item
	\headerrow
	{\textbf{Luxe St.}}
	{\texttt{luxe-st.com/}}
	\\
	\headerrow
	{\emph{Product Design Lead}}
	{\emph{April 2014 -- Present}}
	\begin{itemize*}
		\item Designed user interface, UX, style guide \& branding materials for high-end fashion e-commerce iOS application. 		
		\item Currently developing iOS beta using \textit{Swift}, for distribution in Winter 2016. 
	\end{itemize*}

	\item
	\headerrow
	{\textbf{Barron Roth Photography}}
	{\texttt{barronroth.photography/}}
	
	\begin{itemize*}
		\item Photographer for a variety of clientele from Ariana Grande to Cushman \& Wakefield Commercial Real Estate.
		\item Organically acquired over 10,000 followers on Facebook \& Instagram platforms for business promotion.		
	\end{itemize*}
	
	
\end{itemize}

\hrule
\vspace{-0.9em}
\subsection*{Activities}

\begin{itemize}
	\parskip=0.1em
	
	\item
	\headerrow
	{\textbf{Boston University Student Government}}
	{\texttt{BUStudentGov.com/}}
	\\
	\headerrow
	{\emph{Vice President}}
	{\emph{April 2015 -- Present}}
	\begin{itemize*}
		\item Championed revival of digital presence for BU Student Government by developing website \& redesigning logos.
		\item Led transition of cabinet \& executive board members onto \textit{Slack} for communications \& \textit{Trello} for task management.
		
	\end{itemize*}	
	
	
	
	\item
	\headerrow
	{\textbf{Society of Hispanic Professional Engineers (SHPE)}}
	{\texttt{SHPEBU.org/}}
	\\
	\headerrow
	{\emph{President}}
	{\emph{Fall 2012 -- Present}}
	\begin{itemize*}
		\item Created and maintained a professional online presence for the chapter by creating the website \texttt{SHPEBU.org}.
		\item Attended SHPE 2013 National Conference in Indianapolis, Indiana to represent our chapter on a national level.
		
	\end{itemize*}
	
	\item
	\headerrow
	{\textbf{BU Entrepreneurship Club}}
	{
%	\texttt{make.bu.edu}
	}
	\\
	\headerrow
	{\emph{Mentor -- Startup Challenge}}
	{\emph{October 2013 -- Present}}
	\begin{itemize*}
		\item Served as a mentor for a team of undergraduates participating in BU E-Club's Annual Startup Challenge.
		\item Designed \texttt{TechR.edu}, a non-profit which repurposes technology for 3rd-world usage, winning the 1st Place Prize.
	\end{itemize*}	
		
	
	\item
	\headerrow
		{\textbf{Computer Engineering Club (Make\_BU)}}
		{\texttt{make.bu.edu}}
	\\
	\headerrow
		{\emph{Cofounder}}
		{\emph{October 2013 -- Present}}
	\begin{itemize*}
		\item Cofounded BU's first organization dedicated to hackathons, hosting a weekly hack night for CS practice.
		\item Assisted in organizing and hosting BU's first-annual hackathon, MakeBU, with 500+ attendants from all over New England.
	\end{itemize*}
	
	
\end{itemize}


\hrule
\vspace{-0.9em}
\subsection*{Honors \& Recognitions}

\begin{itemize}
	\parskip=0.001em	
	
	\item
	\headerrow
	{Downtyme -- 1st Place: MIT Beantown Throwdown Startup Competition \& BU ENG Imagineering Competition}
	{
%	\emph{2014}
	}
	
	\item
	\headerrow
	{Dean's Host -- Boston University College of Engineering. Selected among several hundred applicants.}
	{
%	\emph{Spring 2013}
	}

\end{itemize}


\hrule
\vspace{-0.8em}

\subsection*{Technical Skills}



\begin{indentsection}{\parindent}
	\hyphenpenalty=1000
	\begin{description*}
		\item [\itab{Languages:}]
		\tab{Swift, Objective-C, Python, C, \CPP, HTML, CSS, Perl, \LaTeX, MATLAB, Spanish (fluent)}
		\item [\itab{Software:}]
		\tab{Sketch, Principle, Slack, Trello, Asana, Final Cut Pro, Adobe Photoshop, Lightroom, Illustrator}
	\end{description*}
\end{indentsection}

	



\end{document}